### 2011-04-06 docs/enthalpy/enthalpy.tex
checkin some notes about constant gamma EOS

The second equation subtracted from the first gives:
\begin{equation}
  -\frac{D (p - p_0)}{Dt} + (p - p_0)  \nabla \cdot \Ub
\end{equation}

@@

>>>>

The second equation subtracted from the first gives:
\begin{equation} \label{eq:difference between h and e equations}
  \frac{D (p_0 - p)}{Dt} - (p_0 - p)  \nabla \cdot \Ub
\end{equation}

@@

\subsection{Constant $\gamma$ Gas}
Going back to the constant $\gamma$, ideal gas EOS, we can rewrite the
enthalpy equation as a pressure evolution equation
\begin{eqnarray}
  \frac{\partial\rho h}{\partial t} + \nabla\cdot\left(\rho h\Ub\right) &=& \frac{Dp_0}{Dt} + \rho H {} \nonumber\\
  \frac{\gamma}{\gamma-1}\frac{\partial p}{\partial t} + \frac{\gamma}{\gamma-1}\nabla\cdot\left(p\Ub\right) &=& \frac{Dp_0}{Dt} + \rho H {} \nonumber\\
  \frac{Dp}{Dt} &=& -p\nabla\cdot\Ub + \frac{\gamma}{\gamma-1}\left(\frac{Dp_0}{Dt}+\rho H\right) \label{eq:H:pressure evolution}.
\end{eqnarray}
Similarly, we can derive a pressure evolution equation from the energy equation
\begin{equation}
  \frac{Dp}{Dt} = -p\nabla\cdot\Ub - \left(\gamma-1\right)p_0\nabla\cdot\Ub + \rho H \label{eq:e:pressure evolution}
\end{equation}
Now, if we further make the assumption that $p_0$ is constant,
$Dp_0/Dt = 0$, then the divergence constraint for such a gas reduces
to
\begin{equation}
\nabla\cdot\Ub = \frac{\gamma-1}{\gamma p_0}H \label{eq:div constraint for constant gamma}.
\end{equation}
Plugging this back into either of \eqref{eq:H:pressure evolution} or \eqref{eq:e:pressure evolution} gives
\begin{equation}
  \frac{Dp}{Dt} = \frac{\gamma-1}{\gamma}\left(1-\frac{p}{p_0}\right)H. \label{eq:pressure evolution constant gamma}
\end{equation}
If $p_0$ is assumed constant and using \eqref{eq:div constraint for
  constant gamma}, the difference between the enthalpy equation and
the energy equation, \eqref{eq:difference between h and e equations},
can be rewritten as
\[
-\frac{Dp}{Dt} - \frac{\gamma}{\gamma-1}\left(1-\frac{p}{p_0}\right)H = 0,
\]
where the equality holds from \eqref{eq:pressure evolution constant gamma}.
